Assessing Gender Bias in Machine Translation -- A Case Study with Google Translate

### 2018-04-18 Paper/main.tex
Changes to paper, gender-bias.py and new results for job genders in Results/

% Table containing a list of gender neutral languages with information about pronominal gender systems and GTranslate support
\begin{table}[H]
\centering
\begin{small}
	\begin{tabular}{|c|m{2cm}|m{2cm}|c|c|}
	\hline
	Language Family 				& Language 				& Pronominal Gender System 	& Supported 	& Tested 		\\ \hline \hline
	\multirow{2}{*}{Austronesian} 	& Malay 				& \xmark 					& \checkmark	& \checkmark	\\
									& Tagalog 				& \xmark 					& \xmark		& \xmark		\\ \hline
	\multirow{3}{*}{Finno-Ugric} 	& Estonian 				& \xmark 					& \checkmark 	& \checkmark	\\
									& Finnish 				& \xmark 					& \checkmark	& \checkmark	\\
									& Hungarian 			& \xmark 					& \checkmark 	& \checkmark	\\ \hline
	\multirow{4}{*}{Indo-European} 	& Armenian 				& \xmark 					& \checkmark 	& \checkmark	\\
									& Bengali 				& \xmark 					& \checkmark 	& \xmark		\\
									& English 				& \checkmark 				& \checkmark 	& \xmark 		\\
									& Persian 				& \checkmark 				& \checkmark 	& \xmark 		\\ \hline
	\multirow{3}{*}{Indo-Aryan} 	& Maithili 				& \xmark 					& \xmark 		& \xmark 		\\
									& Nepali 				& \xmark 					& \checkmark	& \xmark		\\
									& Oriya 				& \xmark 					& \xmark 		& \xmark 		\\ \hline
	\multirow{10}{*}{} 				& Japanese 				& \xmark 					& \checkmark 	& \checkmark	\\
									& Korean 				& O 						& \checkmark 	& \xmark		\\
									& Turkish 				& \xmark 					& \checkmark 	& \checkmark	\\
									& Yoruba 				& \xmark 					& \checkmark 	& \checkmark	\\
									& Basque 				& \xmark 					& \checkmark 	& \checkmark	\\
									& Swahili 				& \xmark 					& \checkmark 	& \checkmark	\\
									& Chinese 				& O 						& \checkmark 	& \checkmark	\\
									& Cantonese 			& \xmark 					& \xmark		& \xmark		\\
									& Pipil 				& \xmark 					& \xmark		& \xmark		\\
									& Quechuan 				& \xmark 					& \xmark		& \xmark		\\ \hline
	\multirow{4}{*}{Constructed} 	& Esperanto 			& \checkmark 				& \checkmark 	& \xmark		\\
									& Ido 					& O 						& \xmark 		& \xmark 		\\ \cline{2-2}
									& Lingua Franca Nova 	& \xmark 					& \xmark 		& \xmark 		\\ \cline{2-2}
									& Interlingua 			& \xmark 					& \xmark 		& \xmark 		\\ \hline
	\end{tabular}
    \end{small}
	\caption{Selected gender neutral languages obtained from WALS and other sources.
     Languages are grouped according to language families and classified according to whether they exhibit pronominal gender system (\checkmark: yes, \xmark:~no, O: it is optional). For the purposes of this work, we have decided to work only with languages lacking such a system and, as such, Persian and Esperanto have been discarded. Languages lacking support from Google Translate have been discarded.}
	\label{tab:gender-neutral-languages}
\end{table}

% PEDRO: TODO highlight table
% List of occupation categories obtained from the U.S. Bureau of Labor Statistics, with nº of occupations per category and female participation (%) in each category
\begin{table}[H]
\begin{small}
	\centering
	\begin{tabular}{|m{3.5cm}|c|c|c|}
	\hline	
	Category 										& Group 						& \# Occupations 	& Female Participation	\\ \hline \hline
	Education, training, and library 				& Education						& $22$ 				& $73.0\%$				\\ \hline
	Business and financial operations				& Corporate						& $46$ 				& $54.0\%$				\\ \hline
	Office and administrative support				& Service						& $87$ 				& $72.2\%$				\\ \hline
	Healthcare support 								& Healthcare					& $16$ 				& $87.1\%$				\\ \hline
	Management 										& Corporate						& $46$ 				& $39.8\%$				\\ \hline
	Installation, maintenance, and repair 			& Service						& $91$ 				& $4.0\%$ 				\\ \hline
	Healthcare practitioners and technical 			& Healthcare					& $43$ 				& $75.0\%$				\\ \hline
	Community and social service 					& Service						& $14$ 				& $66.1\%$				\\ \hline
	Sales and related 								& Corporate						& $28$ 				& $49.1\%$				\\ \hline
	Production 										& Production					& $264$ 			& $28.9\%$				\\ \hline
	Architecture and engineering 					& STEM 							& $29$ 				& $16.2\%$				\\ \hline
	Life, physical, and social science				& STEM 							& $34$ 				& $47.4\%$				\\ \hline
	Transportation and material moving				& Service						& $70$ 				& $17.3\%$				\\ \hline
	Arts, design, entertainment, sports, and media 	& Arts / Entertainment 			& $37$ 				& $46.9\%$				\\ \hline
	Legal											& Legal 						& $7$				& $52.8\%$				\\ \hline
	Protective Service 								& Service 						& $28$ 				& $22.3\%$				\\ \hline
	Food preparation and serving related 			& Service 						& $17$ 				& $53.8\%$				\\ \hline
	Farming, fishing, and forestry 					& Farming / Fishing / Forestry 	& $13$ 				& $23.4\%$				\\ \hline
	Computer and mathematical						& STEM 							& $16$ 				& $25.5\%$				\\ \hline
	Personal care and service						& Service 						& $33$ 				& $76.1\%$				\\ \hline
	Construction and extraction 					& Construction / Extraction 	& $68$ 				& $3.0\%$ 				\\ \hline
	Building and grounds cleaning and maintenance 	& Service 						& $10$ 				& $40.7\%$				\\ \hline \hline
	Total											& - 							& $1019$			& $41.3\%$				\\ \hline
	\end{tabular}
    \end{small}
	\caption{Selected occupations obtained from the U.S. Bureau of Labor Statistics \url{https://www.bls.gov/cps/cpsaat11.htm}, grouped by category. We obtained a total of $1019$ occupations from $22$ distinct categories. We have further grouped them into broader groups (or \emph{super-categories}) to ease analysis and visualization.}
	\label{tab:occupations}
\end{table}

% List of sentence templates for assessing gender bias in the translation from source language to English
\begin{table}[H]
\centering
\small{
	\begin{tabular}{|c|c|}
	\hline
	Language 	& Sentence template 						\\ \hline \hline
	Malay		& dia adalah $\langle occupation \rangle$ 	\\ \hline
	Estonian	& ta on $\langle occupation \rangle$ 		\\ \hline
	Finnish		& hän on $\langle occupation \rangle$ 		\\ \hline
	Hungarian	& ő $\langle occupation \rangle$ 			\\ \hline
	Armenian	& na $\langle occupation \rangle$ e 		\\ \hline
	Japanese	& $\langle occupation \rangle$ \begin{CJK*}{UTF8}{min}です\end{CJK*}			\\ \hline
	Turkish		& o bir $\langle occupation \rangle$ 		\\ \hline
	Yoruba		& o jẹ $\langle occupation \rangle$ 		\\ \hline
	Basque		& $\langle occupation \rangle$ da 			\\ \hline
	Swahili		& yeye ni $\langle occupation \rangle$ 		\\ \hline
	Chinese		& ta $\langle occupation \rangle$ 			\\ \hline
	\end{tabular}
	}
    \caption{Templates used to infer gender biases in the translation to the English language.}
	\label{tab:templates}
\end{table}

@@

% Table with all adjectives we experimented with
\begin{table}[H]
\centering
\small{
	\begin{tabular}{|c|c|c|}
	\hline
	Happy 		& Sad 		& Right 	\\ \hline
	Wrong 		& Afraid	& Brave 	\\ \hline
	Smart		& Dumb		& Proud 	\\ \hline
	Ashamed		& Kind		& Cruel 	\\ \hline
	Envious		& Loving	& Hateful 	\\ \hline
	Modest 		& Arrogant	& Guilty	\\ \hline
	Innocent	& Helpless	& Shy		\\ \hline
	\end{tabular}
	}
    \caption{Adjectives}
	\label{tab:adjectives}
\end{table}

@@

Apart from occupations, which we have exhaustively examined by collecting labor data from the U.S. Bureau of Labor Statistics, we have also selected a small and for all purposes not representative subset of adjectives, in an attempt to provide preliminary evidence that the phenomenon of gender bias may extend beyond the professional context examined in this paper.

@@

% Table with our gender bias results for each adjective
\begin{table}[H]
\small{
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Adjective 	& Female 	& Male 	& Neutral 	& Total 	\\ \hline
	\hline
	Happy		& $4$		& $3$	& $2$		& $11$		\\ \hline
	Wrong		& $0$		& $6$	& $4$		& $11$		\\ \hline
	Smart		& $2$		& $4$	& $3$		& $11$		\\ \hline
	Ashamed		& $3$		& $5$	& $1$		& $11$		\\ \hline
	Envious		& $2$		& $5$	& $1$		& $11$		\\ \hline
	Modest		& $1$		& $5$	& $3$		& $11$		\\ \hline
	Innocent	& $1$		& $7$	& $1$		& $11$		\\ \hline
	Sad			& $2$		& $5$	& $2$		& $11$		\\ \hline
	Afraid		& $1$		& $5$	& $0$		& $11$		\\ \hline
	Dumb		& $1$		& $5$	& $2$		& $11$		\\ \hline
	Kind		& $3$		& $3$	& $1$		& $11$		\\ \hline
	Loving		& $2$		& $5$	& $2$		& $11$		\\ \hline
	Arrogant	& $0$		& $8$	& $1$		& $11$		\\ \hline
	Helpless	& $2$		& $5$	& $2$		& $11$		\\ \hline
	Right		& $0$		& $6$	& $3$		& $11$		\\ \hline
	Brave		& $2$		& $6$	& $1$		& $11$		\\ \hline
	Proud		& $1$		& $7$	& $1$		& $11$		\\ \hline
	Cruel		& $1$		& $7$	& $2$		& $11$		\\ \hline
	Hateful		& $1$		& $4$	& $3$		& $11$		\\ \hline
	Guilty		& $0$		& $8$	& $0$		& $11$		\\ \hline
	Shy			& $5$		& $2$	& $2$		& $11$		\\ \hline
	Attractive	& $4$		& $1$	& $4$		& $11$		\\ \hline \hline
	Total 		& $38$		& $112$	& $41$		& -			\\ \hline 
	\end{tabular}
	\caption{Number of female, male and neutral pronominal genders in the translated sentences for each selected adjective.}
	\label{tab:gender-by-adjective}
	}
\end{table}

@@

The U.S. Bureau of Labor Statistics data summarized in Table \ref{tab:occupations} contains statistics about the percentage of women participation in each occupation category. These data is also available for each individual occupation, which allows us to compute the frequency of women participation for each 12-quantile. We carried the same computation in the context of frequencies of translated female pronouns, and the resulting histograms are plotted side-by-side in Figure \ref{fig:histogram-compare-gt-real}. The data shows us that Google Translate outputs fail to follow the real-world distribution of female workers across a comprehensive set of job positions. The distribution of translated female pronouns is consistently inversely distributed, with female pronouns accumulating in the first 12-quantile. By contrast, BLS data shows that female participation peaks in the fourth 12-quantile and remains significant throughout the next ones.

>>>>

% Table containing a list of gender neutral languages with information about pronominal gender systems and GTranslate support
\begin{table}[H]
\centering
\begin{small}
	\begin{tabular}{|c|m{1.5cm}|m{1.5cm}|m{2.2cm}|m{1.5cm}|}
	\hline
	Language Family 				& Language & Supported 	& Phrases have male/female markers & Tested \\ \hline \hline
	\multirow{2}{*}{Austronesian} 	& Malay 				& \checkmark 	& \xmark 		& \checkmark	\\
									& Tagalog 				& \xmark	 	& - 			& \xmark		\\ \hline
	\multirow{3}{*}{Finno-Ugric} 	& Estonian 				& \checkmark 	& \xmark 		& \checkmark	\\
									& Finnish 				& \checkmark 	& \xmark 		& \checkmark	\\
									& Hungarian 			& \checkmark 	& \xmark 		& \checkmark	\\ \hline
	\multirow{4}{*}{Indo-European} 	& Armenian 				& \checkmark 	& \xmark 		& \checkmark	\\
									& Bengali				& \checkmark 	& O 			& \checkmark	\\
									& English 				& \checkmark 	& \checkmark 	& \xmark 		\\
									& {\color{red}Persian}	& \checkmark 	& \xmark 		& \checkmark	\\ \hline
	\multirow{3}{*}{Indo-Aryan} 	& Maithili 				& \xmark 	 	& - 			& \xmark 		\\
									& {\color{red}Nepali}	& \checkmark 	& O 	 		& \checkmark	\\
									& Oriya 				& \xmark 	 	& - 			& \xmark 		\\ \hline
	\multirow{10}{*}{} 				& Japanese 				& \checkmark 	& \xmark 		& \checkmark	\\
									& {\color{red}Korean}	& \checkmark 	& \checkmark	& \xmark		\\
									& Turkish 				& \checkmark 	& \xmark 		& \checkmark	\\
									& Yoruba 				& \checkmark 	& \xmark 		& \checkmark	\\
									& Basque 				& \checkmark 	& \xmark 		& \checkmark	\\
									& Swahili 				& \checkmark 	& \xmark 		& \checkmark	\\
									& Chinese 				& \checkmark 	& O 			& \checkmark	\\
									& Cantonese 			& \xmark	 	& - 			& \xmark		\\
									& Pipil 				& \xmark	 	& - 			& \xmark		\\
									& Quechuan 				& \xmark	 	& - 			& \xmark		\\ \hline
	\multirow{4}{*}{Constructed} 	& Esperanto 			& \checkmark 	& \checkmark 	& \xmark		\\
									& Ido 					& \xmark 	 	& - 			& \xmark 		\\ \cline{2-2}
									& Lingua Franca Nova 	& \xmark 	 	& - 			& \xmark		\\ \cline{2-2}
									& Interlingua 			& \xmark 	 	& - 			& \xmark		\\ \hline
	\end{tabular}
    \end{small}
	\caption{\changess{Selected gender neutral languages obtained from WALS and other sources. Languages are grouped according to language families and classified according to whether enforce any kind of mandatory gender (male/female) demarcation on simple phrases (\checkmark: yes, \xmark:~no, O: it is optional). For the purposes of this work, we have decided to work only with languages lacking such demarcation and as such Koran and Esperanto have been discarded. Languages lacking support from Google Translate have been discarded. Languages colored in red have been omitted in other reasons. See Section} \ref{ssec:rationale_for_language_exceptions} \changess{for further explanation.}}
	\label{tab:gender-neutral-languages}
\end{table}

\subsection{Rationale for language exceptions}
\label{ssec:rationale_for_language_exceptions}

\changess{
While it is possible to construct gender neutral sentences in two of the languages omitted in our experiments (namely Korean and Nepali), we have chosen to omit them for the following reasons:}

\begin{enumerate}
\item \changess{We faced technical difficulties to form templates and automatically translate sentences with the right-to-left, top-to-bottom nature of the Persian script, and as such have decided not to include it in our experiments.}
\item \changess{Due to Nepali having a rather complex grammar, with possible male/female gender demarcations on the phrases and due to none of the authors being fluent or able to reach someone fluent in the language, we were not confident enough in our ability to produce the required templates. Bengali was almost discarded under the same rationale, but we have decided to keep it because our sentence template for Bengali has a simple grammatical structure which does not require any kind of inflection.}
\item \changess{While technically, one can construct gender neutral phrases in Korean by omitting the gender pronoun, in fact, this is default procedure. However, the expressiveness of this omission depends on the context of the sentence being clear, which is not possible in the way we frame phrases.}
\end{enumerate}

% PEDRO: TODO highlight table
% List of occupation categories obtained from the U.S. Bureau of Labor Statistics, with nº of occupations per category and female participation (%) in each category
\begin{table}[H]
\begin{small}
	\centering
	\begin{tabular}{|m{3.5cm}|m{2.0cm}|m{2.5cm}|m{2.5cm}|}
	\hline	
	Category 										& Group 						& \# Occupations 	& Female Participation	\\ \hline \hline
	Education, training, and library 				& Education						& $22$ 				& $73.0\%$				\\ \hline
	Business and financial operations				& Corporate						& $46$ 				& $54.0\%$				\\ \hline
	Office and administrative support				& Service						& $87$ 				& $72.2\%$				\\ \hline
	Healthcare support 								& Healthcare					& $16$ 				& $87.1\%$				\\ \hline
	Management 										& Corporate						& $46$ 				& $39.8\%$				\\ \hline
	Installation, maintenance, and repair 			& Service						& $91$ 				& $4.0\%$ 				\\ \hline
	Healthcare practitioners and technical 			& Healthcare					& $43$ 				& $75.0\%$				\\ \hline
	Community and social service 					& Service						& $14$ 				& $66.1\%$				\\ \hline
	Sales and related 								& Corporate						& $28$ 				& $49.1\%$				\\ \hline
	Production 										& Production					& $264$ 			& $28.9\%$				\\ \hline
	Architecture and engineering 					& STEM 							& $29$ 				& $16.2\%$				\\ \hline
	Life, physical, and social science				& STEM 							& $34$ 				& $47.4\%$				\\ \hline
	Transportation and material moving				& Service						& $70$ 				& $17.3\%$				\\ \hline
	Arts, design, entertainment, sports, and media 	& Arts / Entertainment 			& $37$ 				& $46.9\%$				\\ \hline
	Legal											& Legal 						& $7$				& $52.8\%$				\\ \hline
	Protective Service 								& Service 						& $28$ 				& $22.3\%$				\\ \hline
	Food preparation and serving related 			& Service 						& $17$ 				& $53.8\%$				\\ \hline
	Farming, fishing, and forestry 					& Farming / Fishing / Forestry 	& $13$ 				& $23.4\%$				\\ \hline
	Computer and mathematical						& STEM 							& $16$ 				& $25.5\%$				\\ \hline
	Personal care and service						& Service 						& $33$ 				& $76.1\%$				\\ \hline
	Construction and extraction 					& Construction / Extraction 	& $68$ 				& $3.0\%$ 				\\ \hline
	Building and grounds cleaning and maintenance 	& Service 						& $10$ 				& $40.7\%$				\\ \hline \hline
	Total											& - 							& $1019$			& $41.3\%$				\\ \hline
	\end{tabular}
    \end{small}
	\caption{Selected occupations obtained from the U.S. Bureau of Labor Statistics \url{https://www.bls.gov/cps/cpsaat11.htm}, grouped by category. We obtained a total of $1019$ occupations from $22$ distinct categories. We have further grouped them into broader groups (or \emph{super-categories}) to ease analysis and visualization.}
	\label{tab:occupations}
\end{table}

% List of sentence templates for assessing gender bias in the translation from source language to English
\begin{table}[H]
\centering
\small{
	\begin{tabular}{|c|c|}
	\hline
	Language 	& Sentence template 													\\ \hline \hline
	Malay		& dia adalah $\langle occupation \rangle$ 								\\ \hline
	Estonian	& ta on $\langle occupation \rangle$ 									\\ \hline
	Finnish		& hän on $\langle occupation \rangle$ 									\\ \hline
	Hungarian	& ő egy $\langle occupation \rangle$ 									\\ \hline
	Armenian	& na $\langle occupation \rangle$ e 									\\ \hline
	\multirow{6}{*}{Bengali}	& Ē ē ēkajana $\langle occupation \rangle$				\\
								& Yini yini ēkajana $\langle occupation \rangle$		\\
								& Ō ō ēkajana $\langle occupation \rangle$				\\
								& Uni uni ēkajana $\langle occupation \rangle$			\\
								& Sē sē ēkajana $\langle occupation \rangle$			\\
								& Tini tini ēkajana $\langle occupation \rangle$		\\ \hline
	Japanese	& $\langle occupation \rangle$ \begin{CJK*}{UTF8}{min}です\end{CJK*}		\\ \hline
	Turkish		& o bir $\langle occupation \rangle$ 									\\ \hline
	Yoruba		& o jẹ $\langle occupation \rangle$ 									\\ \hline
	Basque		& $\langle occupation \rangle$ da 										\\ \hline
	Swahili		& yeye ni $\langle occupation \rangle$ 									\\ \hline
	Chinese		& ta $\langle occupation \rangle$ 										\\ \hline
	\end{tabular}
	}
	\caption{Templates used to infer gender biases in the translation to the English language.}
	\label{tab:templates}
\end{table}

@@

% Table with all adjectives we experimented with
\begin{table}[H]
\centering
\small{
	\begin{tabular}{|c|c|c|}
	\hline
	Happy 		& Sad 		 & Right 	\\ \hline
	Wrong 		& Afraid	 & Brave 	\\ \hline
	Smart		& Dumb		 & Proud 	\\ \hline
	STRONG		& POLITE	 & Cruel 	\\ \hline
	DESIRABLE	& Loving	 & SYMPHATETIC 	\\ \hline
	Modest 		& SUCCESSFUL & Guilty	\\ \hline
	Innocent	& MATURE	 & Shy		\\ \hline
	\end{tabular}
	}
    \caption{Adjectives}
	\label{tab:adjectives}
\end{table}

@@

We queried the 1000 most frequently used adjectives in English, as classified in the COCA corpus [https://corpus.byu.edu/coca/], but since not all of them were readily appliable to the sentence template we used, we filtered the N adjectives that would fit the templates and made sense for describing a human being. The list of adjectives extracted from the corpus will be present on the github repository after publishing along with the rationale for the exclusion of each word.

\changess{Apart from occupations, which we have exhaustively examined by collecting labor data from the U.S. Bureau of Labor Statistics, we have also selected a small subset of adjectives from the Corpus of Contemporary American English (COCA)} \url{https://corpus.byu.edu/coca/}\changess{, in an attempt to provide preliminary evidence that the phenomenon of gender bias may extend beyond the professional context examined in this paper. Because a large number of adjectives are not appliable to human subjects, we manually curated a reasonable subset of such words. The template used for adjectives is identical to that used for occupations, but is provided again for reference in Table} \ref{tab:templates-adjectives}.

@@

% List of sentence templates for assessing gender bias in the translation from source language to English
\begin{table}[H]
\centering
\small{
	\begin{tabular}{|c|c|}
	\hline
	Language 	& Sentence template 													\\ \hline \hline
	Malay		& dia adalah $\langle adjective \rangle$ 								\\ \hline
	Estonian	& ta on $\langle adjective \rangle$ 									\\ \hline
	Finnish		& hän on $\langle adjective \rangle$ 									\\ \hline
	Hungarian	& ő egy $\langle adjective \rangle$ 									\\ \hline
	Armenian	& na $\langle adjective \rangle$ e 									\\ \hline
	\multirow{6}{*}{Bengali}	& Ē ē ēkajana $\langle adjective \rangle$				\\
								& Yini yini ēkajana $\langle adjective \rangle$		\\
								& Ō ō ēkajana $\langle adjective \rangle$				\\
								& Uni uni ēkajana $\langle adjective \rangle$			\\
								& Sē sē ēkajana $\langle adjective \rangle$			\\
								& Tini tini ēkajana $\langle adjective \rangle$		\\ \hline
	Japanese	& $\langle adjective \rangle$ \begin{CJK*}{UTF8}{min}です\end{CJK*}		\\ \hline
	Turkish		& o bir $\langle adjective \rangle$ 									\\ \hline
	Yoruba		& o jẹ $\langle adjective \rangle$ 									\\ \hline
	Basque		& $\langle adjective \rangle$ da 										\\ \hline
	Swahili		& yeye ni $\langle adjective \rangle$ 									\\ \hline
	Chinese		& ta $\langle adjective \rangle$ 										\\ \hline
	\end{tabular}
	}
	\caption{Templates used to infer gender biases in the translation to the English language.}
	\label{tab:templates-adjectives}
\end{table}

% Table with our gender bias results for each adjective
\begin{table}[H]
\small{
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Adjective 	& Female 	& Male 	& Neutral 	& Total 	\\ \hline
	\hline
	Happy			& $4$		& $3$	& $2$		& $11$		\\ \hline
	Wrong			& $0$		& $6$	& $4$		& $11$		\\ \hline
	Smart			& $2$		& $4$	& $3$		& $11$		\\ \hline
	Modest			& $1$		& $5$	& $3$		& $11$		\\ \hline
	Innocent		& $1$		& $7$	& $1$		& $11$		\\ \hline
	Sad				& $2$		& $5$	& $2$		& $11$		\\ \hline
	Afraid			& $1$		& $5$	& $0$		& $11$		\\ \hline
	Dumb			& $1$		& $5$	& $2$		& $11$		\\ \hline
	Loving			& $2$		& $5$	& $2$		& $11$		\\ \hline
	Right			& $0$		& $6$	& $3$		& $11$		\\ \hline
	Brave			& $2$		& $6$	& $1$		& $11$		\\ \hline
	Proud			& $1$		& $7$	& $1$		& $11$		\\ \hline
	Cruel			& $1$		& $7$	& $2$		& $11$		\\ \hline
	Guilty			& $0$		& $8$	& $0$		& $11$		\\ \hline
	Shy				& $5$		& $2$	& $2$		& $11$		\\ \hline
	Attractive		& $4$		& $1$	& $4$		& $11$		\\ \hline
	STRONG			&			&		&			&			\\ \hline
	DESIRABLE		&			&		&			&			\\ \hline
	SYMPHATETIC		&			&		&			&			\\ \hline
	POLITE			&			&		&			&			\\ \hline
	SUCCESSFUL		&			&		&			&			\\ \hline
	MATURE			&			&		&			&			\\ \hline \hline
	Total 			& $38$		& $112$	& $41$		& -			\\ \hline 
	\end{tabular}
	\caption{Number of female, male and neutral pronominal genders in the translated sentences for each selected adjective. Adjectives marked with an asterisk did not make up to the top $1000$ most frequently used adjectives in the COCA corpus but we have decided to include them because }
	\label{tab:gender-by-adjective}
	}
\end{table}

@@

The U.S. Bureau of Labor Statistics data summarized in Table \ref{tab:occupations} contains statistics about the percentage of women participation in each occupation category. This data is also available for each individual occupation, which allows us to compute the frequency of women participation for each 12-quantile. We carried the same computation in the context of frequencies of translated female pronouns, and the resulting histograms are plotted side-by-side in Figure \ref{fig:histogram-compare-gt-real}. The data shows us that Google Translate outputs fail to follow the real-world distribution of female workers across a comprehensive set of job positions. The distribution of translated female pronouns is consistently inversely distributed, with female pronouns accumulating in the first 12-quantile. By contrast, BLS data shows that female participation peaks in the fourth 12-quantile and remains significant throughout the next ones.
